Bow shocks, bow waves, and dust waves. III. Diagnostics

### 2019-04-12 papers/Papers1234/bs-bw-dw-03.tex
Revised versions of all 4 bow shock papers to astro-ph
Fix reference lists and other minor changes

We have proposed a novel diagnostic method, the \(\tau\)-\(\eta\shell\)
diagram, for analyzing observations of stellar bow shocks around OB
stars, which allows discrimination between radiation-supported and
wind-supported bows.  Our principal results are as follows:
\begin{enumerate}[1.]
\item The UV optical depth \(\tau\) of the bow shell can be estimated
  from the observed infrared shell luminosity \(L\IR\) and stellar
  luminosity \(L_*\) as \(\tau = 2 L\IR/L_*\)
  (\S~\ref{sec:energy-trapp-vers}).
\item The shell momentum efficiency \(\eta\shell\), which is the
  fraction of stellar radiative momentum that is transferred to the
  shell either directly or indirectly (via stellar wind), can be
  estimated from \(\tau\) and the observed shell radius \(R_0\), after
  making some auxiliary assumptions about the physical conditions in
  the shell (\S~\ref{sec:energy-trapp-vers}).
\item By comparing \(\tau\) and \(\eta\shell\), it is possible to
  discriminate between three regimes (\S~\ref{sec:eta-tau-diagnostic}
  and see Paper~I): wind-supported bow shocks
  (\(\eta\shell \gg \tau\)), radiation-supported bow waves
  (\(\eta\shell \sim \tau < 1\)), and radiation-supported bow shocks
  (\(\eta\shell \sim \tau > 1\)).
\item Shells with \(\eta\shell < \num{e-3}\) are potentially in a
  fourth regime of dust waves, where gas--grain collisional coupling
  breaks down (see Paper~II).
\item By analyzing a published sample of 20 mid-infrared bow shock
  candidates \citep[K18]{Kobulnicky:2018a}, plus additional compact
  bows in Orion, we find 4 strong candidates for radiation-supported
  bow waves plus 3 marginal cases (\S\S~\ref{sec:cand-radi-supp} and
  \ref{sec:comm-prop-cand}).  No strong candidates for dust waves are
  found.
\item For wind-supported bow shocks, the stellar wind mass-loss rate
  can be found from \(\tau\) and \(\eta\shell\)
  (\S~\ref{sec:mass-loss-determ}). We compare this method with the
  previously proposed method of K18 (\S~\ref{app:bow-shock-data}) and
  suggest a correction to the dust emissivities used in the latter,
  which reduces the mass-loss rates by a factor of about 2.
\item After this correction, the two mass-loss methods agree well for
  small bows (\(R_0 \le \SI{0.3}{pc}\)), but the
  \(\tau\)--\(\eta\shell\) method under-predicts the mass-loss rate by
  up to a factor of 10 for larger bows, which also tend to have
  relatively thin shells (\S~\ref{sec:underst-diff-betw}).  This
  discrepancy could be eliminated by extending the
  \(\tau\)--\(\eta\shell\) method to include the observed shell
  thickness.
\item Disruption of the largest dust grains by rotational torques in
  the strong circumstellar radiation field is predicted to have a
  relatively modest effect on the optical properties of the dust
  mixture (\S~\ref{sec:evolution-grain-size}), increasing the UV
  opacity by about 50\%.
\item The bow source KGK2010~2 is a low-luminosity B~star with an
  anomalously high apparent mass-loss rate.  This discrepancy could be
  eliminated if the bow shell has trapped the ionization front and is
  predominantly neutral, in which case it would become yet another
  candidate for radiation support.
\end{enumerate}

\section*{Acknowledgements}
We are grateful for financial support provided by Dirección General de
Asuntos del Personal Académico, Universidad Nacional Autónoma de
México, through grant Programa de Apoyo a Proyectos de Investigación e
Inovación Tecnológica IN107019.  This work has made extensive use of
Python language libraries from the SciPy \citep{Jones:2001a}, AstroPy
\citep{Astropy-Collaboration:2013a, Astropy-Collaboration:2018a} and
Pandas \citep{McKinney:2010a} projects.  We thank Chip Kobulnicky for
sharing results in advance of publication.

>>>>

We have proposed a novel diagnostic method, the \(\tau\)-\(\eta\shell\)
diagram, for analyzing observations of stellar bow shocks around OB
stars, which allows discrimination between radiation-supported and
wind-supported bows.  Our principal results are as follows:
\begin{enumerate}[1.]
\item The UV optical depth \(\tau\) of the bow shell can be estimated
  from the observed infrared shell luminosity \(L\IR\) and stellar
  luminosity \(L_*\) as \(\tau = 2 L\IR/L_*\)
  (\S~\ref{sec:energy-trapp-vers}).
\item The shell momentum efficiency \(\eta\shell\), which is the
  fraction of stellar radiative momentum that is transferred to the
  shell either directly or indirectly (via stellar wind), can be
  estimated from \(\tau\) and the observed shell radius \(R_0\), after
  making some auxiliary assumptions about the physical conditions in
  the shell (\S~\ref{sec:energy-trapp-vers}).
\item By comparing \(\tau\) and \(\eta\shell\), it is possible to
  discriminate between three regimes (\S~\ref{sec:eta-tau-diagnostic}
  and see Paper~I): wind-supported bow shocks
  (\(\eta\shell \gg \tau\)), radiation-supported bow waves
  (\(\eta\shell \sim \tau < 1\)), and radiation-supported bow shocks
  (\(\eta\shell \sim \tau > 1\)).
\item Shells with \(\eta\shell < \num{e-3}\) are potentially in a
  fourth regime of dust waves, where gas--grain collisional coupling
  breaks down (see Paper~II).
\item By analyzing a published sample of 20 mid-infrared bow shock
  candidates \citep[K18]{Kobulnicky:2018a}, plus additional compact
  bows in Orion, we find 4 strong candidates for radiation-supported
  bow waves plus 3 marginal cases (\S\S~\ref{sec:cand-radi-supp} and
  \ref{sec:comm-prop-cand}).  No strong candidates for dust waves are
  found.
\item For wind-supported bow shocks, the stellar wind mass-loss rate
  can be found from \(\tau\) and \(\eta\shell\)
  (\S~\ref{sec:mass-loss-determ}). We compare this method with the
  previously proposed method of K18 (\S~\ref{app:bow-shock-data}) and
  suggest a correction to the dust emissivities used in the latter,
  which reduces the mass-loss rates by a factor of about 2.
\item After this correction, the two mass-loss methods agree well for
  small bows (\(R_0 \le \SI{0.3}{pc}\)), but the
  \(\tau\)--\(\eta\shell\) method under-predicts the mass-loss rate by
  up to a factor of 10 for larger bows, which also tend to have
  relatively thin shells (\S~\ref{sec:underst-diff-betw}).  This
  discrepancy could be eliminated by extending the
  \(\tau\)--\(\eta\shell\) method to include the observed shell
  thickness.
% \item Disruption of the largest dust grains by rotational torques in
%   the strong circumstellar radiation field is predicted to have a
%   relatively modest effect on the optical properties of the dust
%   mixture (\S~\ref{sec:evolution-grain-size}), increasing the UV
%   opacity by about 50\%.
\item Disruption of the largest dust grains by rotational torques in
  the strong circumstellar radiation field is predicted to increase
  the UV opacity by about 50\% (\S~\ref{sec:evolution-grain-size}),
  although the effect could be larger if the resulting fragments are
  very small.
\item The bow source KGK2010~2 is a low-luminosity B~star with an
  anomalously high apparent mass-loss rate.  This discrepancy could be
  eliminated if the bow shell has trapped the ionization front and is
  predominantly neutral, in which case it would become yet another
  candidate for radiation support.
\end{enumerate}

\section*{Acknowledgements}
We are grateful for financial support provided by Dirección General de
Asuntos del Personal Académico, Universidad Nacional Autónoma de
México, through grant Programa de Apoyo a Proyectos de Investigación e
Inovación Tecnológica IN107019.  This work has made extensive use of
Python language libraries from the SciPy \citep{Jones:2001a}, AstroPy
\citep{Astropy-Collaboration:2013a, Astropy-Collaboration:2018a} and
Pandas \citep{McKinney:2010a} projects.  We thank Chip Kobulnicky for
sharing results in advance of publication and Thiem Hoang for useful
discussions.
